### 2025-07-03 index.qmd
20250703 - types of regression

# Automatically create a bib database for R packages
packagesForBibliography <- c(
  "petersenlab", "ffanalytics",
  "knitr", "rmarkdown", "dplyr", "ggplot2", "tidyverse", "broom", "broom.mixed", 
  "downlit", "xml2", "nflreadr", "nflplotR", "nflfastR", "nflseedR", "nfl4th", 
  "gsisdecoder", "progressr", "DescTools", "pwr", "pwrss", "WebPower", "XICOR", 
  "dagitty", "ggdag", "lubridate", "ggtext", "gghighlight", "ggExtra", "grid", 
  "patchwork", "pROC",  "lme4", "lmerTest", "MuMIn", "emmeans", "pbkrtest", 
  "sjstats", "AICcmodavg", "rstan", "brms", "tidybayes", "bbmle", 
  "fitdistrplus", "sn", "mclust", "magrittr", "viridis", "plotly", "quantmod", 
  "fPortfolio", "NMOF", "xts", "zoo", "forecast", "stringi", "parallel", #"webshot2"
  "parallelly", "doParallel", "missRanger", "ggridges", "powerjoin", "caret", 
  "gpboost", "cmdstanr", "learnr", "remotes", "corrplot", "correlation", "mgcv", 
  "rms", "car", "performance", "lavaan", "mice", "miceadds", "interactions", 
  "shiny", "PearsonDS", "robustbase", "data.table", "future", "future.apply", 
  "QuantPsyc", "SimDesign"
)

>>>>

# Automatically create a bib database for R packages
packagesForBibliography <- c(
  "petersenlab", "ffanalytics",
  "knitr", "rmarkdown", "dplyr", "ggplot2", "tidyverse", "broom", "broom.mixed", 
  "downlit", "xml2", "nflreadr", "nflplotR", "nflfastR", "nflseedR", "nfl4th", 
  "gsisdecoder", "progressr", "DescTools", "pwr", "pwrss", "WebPower", "XICOR", 
  "dagitty", "ggdag", "lubridate", "ggtext", "gghighlight", "ggExtra", "grid", 
  "patchwork", "pROC",  "lme4", "lmerTest", "MuMIn", "emmeans", "pbkrtest", 
  "sjstats", "AICcmodavg", "rstan", "brms", "tidybayes", "bbmle", 
  "fitdistrplus", "sn", "mclust", "magrittr", "viridis", "plotly", "quantmod", 
  "fPortfolio", "NMOF", "xts", "zoo", "forecast", "stringi", "parallel", #"webshot2"
  "parallelly", "doParallel", "missRanger", "ggridges", "powerjoin", "caret", 
  "tidymodels", "LongituRF", "gpboost", "cmdstanr", "learnr", "remotes", 
  "corrplot", "correlation", "mgcv", "rms", "car", "performance", "lavaan", 
  "mice", "miceadds", "interactions", "shiny", "PearsonDS", "robustbase", 
  "ordinal", "MASS", "data.table", "future", "future.apply", "QuantPsyc", 
  "SimDesign", "effectsize"
)

### 2025-07-03 multiple-regression.qmd
20250703 - types of regression

```{r}
library("petersenlab")
library("rms")
library("car")
library("caret")
library("lme4")
library("performance")
library("lavaan")
library("mice")
library("miceadds")
library("interactions")
library("brms")
library("robustbase")
library("broom")
library("tidyverse")
library("knitr")
```

@@

>>>>

```{r}
library("petersenlab")
library("rms")
library("car")
library("caret")
library("lme4")
library("performance")
library("lavaan")
library("mice")
library("miceadds")
library("interactions")
library("brms")
library("robustbase")
library("ordinal")
library("MASS")
library("broom")
library("tidyverse")
library("knitr")
```

@@

## Types of Regression {#sec-multipleRegressionTypes}

When the outcome variable is continuous, [linear regression](#sec-multipleRegressionLinear) is common.
However, there are other types of regression depending on type and distribution of the [outcome variable](#sec-correlationalStudy).
For instance, if the [outcome variable](#sec-correlationalStudy) is binary, [logistic regression](#sec-multipleRegressionLogistic) would be used.
If the [outcome variable](#sec-correlationalStudy) is an ordered categorical variable, [ordinal regression](#sec-multipleRegressionOrdinal) would be used.
If the [outcome variable](#sec-correlationalStudy) is a count, [Poisson](#sec-multipleRegressionPoisson) or [negative binomial](#sec-multipleRegressionNegativeBinomial) regression would be preferable.
If the [outcome variable](#sec-correlationalStudy) is a proportion, [beta regression](#sec-multipleRegressionBeta) would be used.

Here are examples of each:

### Linear Regression {#sec-multipleRegressionLinear}

```{r}
linearRegression <- lm(
  fantasyPoints ~ age + height + weight + target_share,
  data = player_stats_seasonal %>% filter(position %in% c("WR")),
  na.action = "na.exclude"
)

summary(linearRegression)
```

### Logistic Regression {#sec-multipleRegressionLogistic}

```{r}
newdata <- player_stats_weekly %>%
  mutate( # create a binary variable to be used as the outcome variable
    receiving_td = case_when(
      is.na(receiving_tds) ~ NA_real_, # keep NA
      receiving_tds >= 1   ~ 1,
      receiving_tds == 0   ~ 0
    )
  )

logisticRegression <- glm(
  receiving_td ~ age + height + weight + target_share,
  data = newdata %>% filter(position %in% c("WR")),
  family = binomial(),
  na.action = "na.exclude"
)

summary(logisticRegression)
```

### Ordinal Regression {#sec-multipleRegressionOrdinal}

```{r}
newdata <- player_stats_weekly
newdata$receiving_tdsFactor <- factor(newdata$receiving_tds, ordered = TRUE)
table(newdata$receiving_tdsFactor)

ordinalRegression <- ordinal::clm(
  receiving_tdsFactor ~ age + height + target_share,
  data = newdata %>% filter(position %in% c("WR")),
  na.action = "na.exclude"
)

summary(ordinalRegression)
```

### Poisson Regression {#sec-multipleRegressionPoisson}

```{r}
poissonRegression <- glm(
  receiving_tds ~ age + height + weight + target_share,
  data = newdata %>% filter(position %in% c("WR")),
  family = poisson(),
  na.action = na.exclude
)

summary(poissonRegression)
```

### Negative Binomial Regression {#sec-multipleRegressionNegativeBinomial}

```{r}
negativeBinomialRegression <- MASS::glm.nb(
  receiving_tds ~ age + height + weight + target_share,
  data = newdata %>% filter(position %in% c("WR")),
  na.action = na.exclude,
  control = glm.control(maxit = 10000)
)

summary(negativeBinomialRegression)
```

### Beta Regression {#sec-multipleRegressionBeta}

betaRegression <- brm(
  formula = target_share ~ age + height + weight,
  data = newdata %>% filter(position %in% c("WR")),
  family = zero_one_inflated_beta(),
)
```

```{r}
summary(betaRegression)
```
